Storm surges in the Strait of Georgia simulated with a regional model

### 2015-01-03 AO_guides/manuscriptAO.tex
Youyu's comment about nonIB oscillations. Added references he suggested

The ocean surface is forced with momentum and heat fluxes from a 33-km global atmospheric reforecasting model suitable for use in ocean modelling \citep{smith2014new}. Forecasts from the period of 2002-2012 are available. One simulation employs the western Canada component of the High Resolution Deterministic Prediction System (HRDPS), a nested 2.5 km resolution atmospheric model provided by Environment Canada \citep{ECModel}. In addition to momentum and heat fluxes, forcing due to the local atmospheric pressure is also included by calculating an inverse barometer sea surface height,
\begin{equation}
 \eta_{IB} = -\frac{1}{g\rho_{0}}\left(P_{s}-P_0\right), \label{eq:inverse}
\end{equation}
where $g$ is the accelaration due to gravity, $\rho_{0}$ is a reference density set to 1035 kg m$^{-3}$, $P_{s}$ is the sea level atmospheric pressure from the atmospheric model, and $P_0$ is a reference sea level pressure set to 101,000 Pa.  The gradient of $\eta_{IB}$  is scaled by $g$ and added to the forcing terms in the ocean momentum equations \citep{madec2012nemo}. Since the atmospheric model employs a terrain following vertical coordinate the model surface pressure has been corrected to sea level using \citep{holton1992introduction}
\[ P_s = P_1\left(\gamma\frac{z_1}{T_1} +1 \right)^\frac{g}{\gamma R},\]
where $P_1$ and $T_1$ are the model pressure and temperature at height $z_1$, $R$ is the ideal gas constant, and $\gamma$ is an temperature lapse rate set to 0.0098 K m$^{-1}$.

>>>>

The ocean surface is forced with momentum and heat fluxes from a 33-km global atmospheric reforecasting model suitable for use in ocean modelling \citep{smith2014new}. Forecasts from the period of 2002-2012 are available. One simulation employs the western Canada component of the High Resolution Deterministic Prediction System (HRDPS), a nested 2.5 km resolution atmospheric model provided by Environment Canada \citep{ECModel}. In addition to momentum and heat fluxes, forcing due to the local atmospheric pressure is also included by calculating an inverse barometer sea surface height,
\begin{equation}
 \eta_{IB} = -\frac{1}{g\rho_{0}}\left(P_{s}-P_0\right), \label{eq:inverse}
\end{equation}
where $g$ is the accelaration due to gravity, $\rho_{0}$ is a reference density set to 1035 kg m$^{-3}$, $P_{s}$ is the sea level atmospheric pressure from the atmospheric model, and $P_0$ is a reference sea level pressure set to 101,000 Pa.  The gradient of $\eta_{IB}$  is scaled by $g$ and added to the forcing terms in the ocean momentum equations \citep{madec2012nemo}. Since the atmospheric model employs a terrain following vertical coordinate the model surface pressure has been corrected to sea level using \citep{holton1992introduction}
\[ P_s = P_1\left(\gamma\frac{z_1}{T_1} +1 \right)^\frac{g}{\gamma R},\]
where $P_1$ and $T_1$ are the model pressure and temperature at height $z_1$, $R$ is the ideal gas constant, and $\gamma$ is a temperature lapse rate set to 0.0098 K m$^{-1}$. Since the model domain does not include the open Pacific Ocean, pressure gradients between the open ocean and the semi-enclosed Salish Sea and their effect in the sea surface height cannot be accounted for. Previous studies in the Hudson Bay and Laborador Shelf system have aruged that oscillations in the sea surface height can be expained, in part, by the response to the pressure gradient between these regions \citep{wright1987influence,young1995synoptic}.
